### 2020-02-13 README.Rmd
Created buffer for SCBI

@@

```{r, cache = TRUE}
square <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()
buffer <- square %>% 
  st_buffer(dist = -0.1)
ggplot() +
  geom_sf(data = square) +
  geom_sf(data = buffer, col="red")

# Bigwoods study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

@@

# Sample of 5000 trees
set.seed(76)
bw_trees_sample <- bw_growth_df %>% 
  sample_n(5000) %>% 
  select(x = gx, y = gy) %>% 
  st_as_sf(coords = c("x", "y"))

index <- st_intersects(bw_trees_sample, bw_buffer, sparse = FALSE)
bw_trees_sample <- bw_trees_sample %>% 
  mutate(buffer = index)

# Plot
ggplot() +
  geom_sf(data = bw_boundary) +
  geom_sf(data = bw_buffer, col="red") +
  geom_sf(data = bw_trees_sample, aes(col=buffer), size = 0.5)
```

@@

```{r, cache = TRUE}
```

>>>>

**Example of buffer at work**:

```{r, cache = TRUE}
# Boundary polygon
square_boundary <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()

# Buffer polygon
square_buffer <- square_boundary %>% 
  st_buffer(dist = -0.1)

ggplot() +
  geom_sf(data = square_boundary) +
  geom_sf(data = square_buffer, col="red") 
```

@@

```{r, cache = TRUE}
# Bigwoods study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

@@

# Convert data frame to sf object
bw_growth_df <- bw_growth_df %>% 
  st_as_sf(coords = c("gx", "gy"))

# ID which points are in buffer and which are not
index <- st_intersects(bw_growth_df, bw_buffer, sparse = FALSE)
bw_growth_df <- bw_growth_df %>% 
  mutate(buffer = index)

# Plot
ggplot() +
  geom_sf(data = bw_boundary) +
  geom_sf(data = bw_buffer, col="red") +
  # Only random sample of 1000 trees:
  geom_sf(data = bw_growth_df %>% sample_n(1000), aes(col=buffer), size = 0.5)
```

@@

```{r, cache = TRUE}
# Bigwoods study region boundary polygon
scbi_boundary <- tibble(
  x = c(0, 0, 400, 400, 0),
  y = c(0, 640, 640, 0, 0)
) %>% 
  sf_polygon()

# Buffer polygon
scbi_buffer <- scbi_boundary %>%
  st_buffer(dist = -max_dist)

# Convert data frame to sf object
scbi_growth_df <- scbi_growth_df %>% 
  st_as_sf(coords = c("gx", "gy"))

# ID which points are in buffer and which are not
index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = index)

# Plot
ggplot() +
  geom_sf(data = scbi_boundary) +
  geom_sf(data = scbi_buffer, col="red") +
  # Only random sample of 1000 trees:
  geom_sf(data = scbi_growth_df %>% sample_n(1000), aes(col=buffer), size = 0.5)
```
